Calendar-based graphics for visualising people's daily schedules

### 2017-07-17 main.Rmd
tweaks of abstract

---
author:
  - name: Earo Wang
    affiliation: Monash University
    address: >
      Department of Econometrics and Business Statistics,
      Monash University, VIC 3800
      Australia
    email: \email{earo.wang@monash.edu}
  - name: Dianne Cook
    affiliation: Monash University
    address: >
      Department of Econometrics and Business Statistics,
      Monash University, VIC 3800
      Australia
    email: \email{dicook@monash.edu}
  - name: Rob J Hyndman
    affiliation: Monash University
    address: >
      Department of Econometrics and Business Statistics,
      Monash University, VIC 3800
      Australia
    email: \email{rob.hyndman@monash.edu}
title:
  formatted: "Calendar-based graphics for visualising people's daily schedules"
  plain: "Calendar-based graphics for visualising people's daily schedules"
abstract: >
  It is challenging to visualise people's daily schedules as such data are often of multiple seasons and of long time span. One example is Melbourne pedestrian sensor data which are collected at hourly interval and at a number of locations. Owing to human activities, the data features multiple temporal scales such as time of day, day of week, day of year. We develop the \code{frame\_calendar} function that provides a method for rearranging such kind of data in a calendar-based format and accomplishing visualisation with the grammar of graphics. We describe its construction along with a few options. We provide some variations to demonstrate its usage by applying to the pedetrian data over one-year period of 2016.
keywords:
  # at least one keyword must be supplied
  formatted: [calendar-based visualisation, temporal-context data]
  plain:     [calendar-based visualisation, temporal-context data]
preamble: >
  \usepackage{amsmath}
output: 
  rticles::jss_article:
  citation_package: biblatex
bibliography: ["references.bib", "packages.bib"]
---

@@

1. Variations primarily result from multiple time scales including time of day, day of week, and day of year (such as public holiday and recurred events).
<!-- 2. Temporal data plots should be arranged in a way that serves a familiar format to viewers. -->
2. Since the data are often collected at daily frequency or a time scale more frequent than daily, they typically involve a large number of observations spanning over a long time period.
3. Measurements of a single type are made at multiple locations at a given time point, which creates the need in comparing and contrasting between locations.

@@

A collection of data plots, organised in a familiar format, offer a useful and intuitive way to tell a richer story and reveal more complex relationships. @Wickham2012glyph embedded a sequence of daily temperature line charts into a glyph map according to the spatial locations; and @R-geofacet provided methods to arrange the data plots of many types into a preserved geographical grid. They both attempt to have the self-contained data plots in spatial context.

>>>>

---
author:
  - name: Earo Wang
    affiliation: Monash University
    address: >
      Department of Econometrics and Business Statistics,
      Monash University, VIC 3800
      Australia
    email: \email{earo.wang@monash.edu}
  - name: Dianne Cook
    affiliation: Monash University
    address: >
      Department of Econometrics and Business Statistics,
      Monash University, VIC 3800
      Australia
    email: \email{dicook@monash.edu}
  - name: Rob J Hyndman
    affiliation: Monash University
    address: >
      Department of Econometrics and Business Statistics,
      Monash University, VIC 3800
      Australia
    email: \email{rob.hyndman@monash.edu}
title:
  formatted: "Calendar-based graphics for visualising people's daily schedules"
  plain: "Calendar-based graphics for visualising people's daily schedules"
abstract: >
  We develop the \code{frame\_calendar} function that provides a method for arranging the data, which are collected at daily frequency or a time scale more frequent than daily, in a calendar-based format and accomplishes visualisation with the grammar of graphics. The calendar-based layout serves as a familiar format for the Western world and it is particularly useful to visualise people's daily schedules. One example is Melbourne pedestrian counts which are captured at hourly interval by a number of sensors. Owing to human activities, the data feature multiple temporal scales such as time of day, day of week, day of year. We describe its construction along with a few options. We provide some variations to demonstrate its usage by applying to the pedetrian data over one-year period of 2016.
keywords:
  # at least one keyword must be supplied
  formatted: [calendar-based visualisation, temporal-context data]
  plain:     [calendar-based visualisation, temporal-context data]
preamble: >
  \usepackage{amsmath}
output: 
  rticles::jss_article:
  citation_package: biblatex
bibliography: ["references.bib", "packages.bib"]
---

@@

1. Variations primarily result from multiple time scales including time of day, day of week, and day of year (such as public holiday and recurred events).
2. Since the data are often collected at daily frequency or a time scale more frequent than daily, they typically involve a large number of observations spanning over a long time period.
3. Measurements of a single type are made at multiple locations at a given time point, which creates the need in comparing and contrasting between locations.

@@

A collection of data plots, organised in a familiar format, offer a useful and intuitive way to tell a richer story and reveal more complex relationships. @Wickham2012glyph embedded a sequence of daily temperature line charts into a glyph map according to the spatial locations; and @R-geofacet provided methods to arrange the data plots of many types into a preserved geographical grid in the \pkg{geofacet} package. They both attempt to have the self-contained data plots in spatial context.

### 2017-07-17 main.tex
tweaks of abstract

\Abstract{
It is challenging to visualise people's daily schedules as such data are
often of multiple seasons and of long time span. One example is
Melbourne pedestrian sensor data which are collected at hourly interval
and at a number of locations. Owing to human activities, the data
features multiple temporal scales such as time of day, day of week, day
of year. We develop the \code{frame\_calendar} function that provides a
method for rearranging such kind of data in a calendar-based format and
accomplishing visualisation with the grammar of graphics. We describe
its construction along with a few options. We provide some variations to
demonstrate its usage by applying to the pedetrian data over one-year
period of 2016.
}

@@

A collection of data plots, organised in a familiar format, offer a
useful and intuitive way to tell a richer story and reveal more complex
relationships. \citet{Wickham2012glyph} embedded a sequence of daily
temperature line charts into a glyph map according to the spatial
locations; and \citet{R-geofacet} provided methods to arrange the data
plots of many types into a preserved geographical grid. They both
attempt to have the self-contained data plots in spatial context.

>>>>

\Abstract{
We develop the \code{frame\_calendar} function that provides a method
for arranging the data, which are collected at daily frequency or a time
scale more frequent than daily, in a calendar-based format and
accomplishes visualisation with the grammar of graphics. The
calendar-based layout serves as a familiar format for the Western world
and it is particularly useful to visualise people's daily schedules. One
example is Melbourne pedestrian counts which are captured at hourly
interval by a number of sensors. Owing to human activities, the data
feature multiple temporal scales such as time of day, day of week, day
of year. We describe its construction along with a few options. We
provide some variations to demonstrate its usage by applying to the
pedetrian data over one-year period of 2016.
}

@@

A collection of data plots, organised in a familiar format, offer a
useful and intuitive way to tell a richer story and reveal more complex
relationships. \citet{Wickham2012glyph} embedded a sequence of daily
temperature line charts into a glyph map according to the spatial
locations; and \citet{R-geofacet} provided methods to arrange the data
plots of many types into a preserved geographical grid in the
\pkg{geofacet} package. They both attempt to have the self-contained
data plots in spatial context.
